### 2021-07-21 paper/localpsf.tex
edits to rational positive definite section based on feedback from J

Together, equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, \eqref{eq:desired_property_3},  and \eqref{eq:desired_property_4}, and the condition $\mu > |\lambda_\text{min}|$, imply that $f(0)=0$ is the unique minimum of $f$ on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that $f$ is non-negative on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that  $f(\widetilde{\mathbf{A}}_\text{sym}) = \widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. The equation $f(0)=0$ implies that the null space of $\widetilde{\mathbf{A}}_\text{sym}^+$ contains the null-space of $\widetilde{\mathbf{A}}_\text{sym}$. This is important when the operator $\mathcal{A}$ has a large (or infinite) dimensional null space, or a spectrum that clusters at zero. Hessians in ill-posed distributed parameter inverse problems typically have both of these properties. The equation $f(\lambda_\text{max})=\lambda_\text{max}$ forces the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ to be close to the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$. I.e., $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. The equation $f(\lambda_\text{min})=|\lambda_\text{min}|$ ensures that the negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, which result from error in the product-convolution approximation, do not get amplified in magnitude by the function $f$. There is a tradeoff: if we choose a larger value for $f(\lambda_\text{min})$, then the positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ will be closer to the corresponding positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ (good), but the erroneous negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ will be amplified more in magnitude (bad). This is shown in Figure FIG. We find that $f(\lambda_\text{min})=|\lambda_\text{min}|$ is an appropriate balance between these competing interests.

>>>>

Together, equations \eqref{eq:desired_property_1}, \eqref{eq:desired_property_2}, \eqref{eq:desired_property_3},  and \eqref{eq:desired_property_4}, and the condition $\mu > |\lambda_\text{min}|$, imply that $f(0)=0$ is the unique minimum of $f$ on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that $f$ is non-negative on $[\lambda_\text{min},\lambda_\text{max}]$, which implies that  $f(\widetilde{\mathbf{A}}_\text{sym}) = \widetilde{\mathbf{A}}_\text{sym}^+$ is positive semi-definite. The equation $f(0)=0$ implies that the null space of $\widetilde{\mathbf{A}}_\text{sym}^+$ contains the null-space of $\widetilde{\mathbf{A}}_\text{sym}$. This is important when the operator $\mathcal{A}$ has a large (or infinite) dimensional null space, or a spectrum that clusters at zero. Hessians in ill-posed distributed parameter inverse problems typically have both of these properties. The equation $f(\lambda_\text{max})=\lambda_\text{max}$ forces the moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ to be close to the corresponding moderate and large positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$. I.e., $f$ modifies the ``important'' part of the spectrum of $\widetilde{\mathbf{A}}_\text{sym}$ as little as possible. The equation $f(\lambda_\text{min})=|\lambda_\text{min}|$ ensures that the negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$, which result from error in the product-convolution approximation, do not get amplified in magnitude by the function $f$. There is a tradeoff: if we choose a larger value for $f(\lambda_\text{min})$, then the positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}^+$ will be closer to the corresponding positive eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ (good), but the erroneous negative eigenvalues of $\widetilde{\mathbf{A}}_\text{sym}$ will be amplified in magnitude (bad). This is shown in Figure FIG. We find that $f(\lambda_\text{min})=|\lambda_\text{min}|$ is an appropriate balance between these competing interests.
